---
title: ''
output: html_document
---

This script will convert the case status of antigen-only positive COVID-19 cases from "confirmed" to "probable". Prior to running the script, download the report "COVID Lab Test Type" from Business Objects and ensure it is stored in your Downloads folder. Change 'downloads_path' below to match the file path of your Downloads folder. If using a Windows machine, be sure to convert backward slashes to forward slashes in the file path.

If running the script for the first time on a given computer, also run the commented out lines on line 25-26 and 66-67.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(RSelenium)
library(magrittr)
library(keyring)

#Source helper rselenium functions from github
devtools::source_url("https://github.com/hsteinberg/ccdph-functions/blob/master/general-use-rselenium-functions.R?raw=TRUE")
devtools::source_url("https://github.com/hsteinberg/ccdph-functions/blob/master/inedss-rselenium-functions.R?raw=TRUE")

downloads_path <- "C:/Users/kbemis/Downloads"

#Create empty already done file -- ONLY NEEDS TO BE DONE THE FIRST TIME RUNNING THE SCRIPT ON A COMPUTER
# already_done <- data.frame(state_case_number = character(), date_updated = as.Date(character()), stringsAsFactors = F)
# saveRDS(already_done, paste0("recently_updated.rds")


```

Use the Business Objects report to identify which confirmed cases have an antigen test but no PCR test.

```{r prepare_data}

#Import BO report and remove duplicates
cases_to_update <- read_csv(paste0(downloads_path, "/COVID_Lab_Test_Type.csv")) %>%
  set_colnames(c("state_case_number", "test_types", "test_methods")) %>%
  distinct()

#Convert to observation level data set
cases_to_update_wide <- cases_to_update %>%
  group_by(state_case_number) %>%
  summarize(all_test_types = paste(test_types, collapse = "-"),
            all_test_methods = paste(test_methods, collapse = "-")) %>%
  ungroup()

#Filter to cases with antigen tests and flag if a pcr test is also present
antigen_cases <- cases_to_update_wide %>%
  filter(grepl("2 ag|antigen|sofia|sophia", all_test_types, ignore.case = T)) %>%
  mutate(has_pcr = grepl("rna|pcr|nucleic|naa|nat|abbott id|gene|molecular|ORF1ab", all_test_types, ignore.case = T))

#To account for BO lag, import list of cases already updated in the last 7 days
already_done <- readRDS("recently_updated.rds") %>%
  filter(date_updated > (Sys.Date() - 7))

#Filter to antigen cases with no pcr test that haven't already been updated
antigen_no_pcr <- filter(antigen_cases, has_pcr == F & !(state_case_number %in% already_done$state_case_number))


```

Use Selenium to log into INEDSS, search each identified case, and change the case status from confirmed to probable.

```{r update_status}

#set inedss login credentials- only needs to be done once per user per computer
#key_set("idph_username") #IDPH username
#key_set("idph_portal") #IDPH password

#Start server
start_server()

#Log in to INEDSS
login_inedss()

#loop to search cases and change case status
continue = TRUE
counter = 1
while(continue) {
  
  try(for (i in counter:nrow(antigen_no_pcr)) {

    #enter SCN in Dash Board search bar and search
    enter_text("#idNumber", antigen_no_pcr[i, 1])
    click(name.is("Search"))
  
    #wait for Case Summary page to load
    wait_page("Case Summary")
  
    #Click to open Epidemiologic Data
    click("fieldset.fieldsetHeader:nth-child(4) > table:nth-child(2) > tbody:nth-child(1) > tr:nth-child(3) > td:nth-child(2) > a:nth-child(1)")
    wait_page("Epidemiologic Data")
  
    #Change case status to probable and save section
    select_drop_down("#case", "Probable")
    click(name.is("save"))
  
    #Wait for Case Summary page to load then return to Dash Board
    wait_page("Case Summary")
    click("th.dataTableNotSelected:nth-child(1) > a:nth-child(1)")
    wait_page("Dash Board")
    
    #Increment counter
    counter <- counter + 1
  
  })
  
  continue = ifelse(counter < nrow(antigen_no_pcr), TRUE, FALSE)
  
}


#stop server when finished
stop_server()

```

Execute final steps to prepare for the next run of the program.

```{r clean_up}

#update already done file
done_today <- antigen_no_pcr %>%
  select(state_case_number) %>%
  mutate(date_updated = Sys.Date())

saveRDS(rbind(already_done, done_today), "recently_updated.rds")

#remove original download
unlink(paste0(downloads_path, "/COVID_Lab_Test_Type.csv"))

```

